---
title: "Regression"
author: "Anna Yeaton"
date: "Fall 2019"
output:
  html_document:
    df_print: paged
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = T)
```

# Lab Section

In this lab, we will go over regression. We will be using the caret package in R. https://topepo.github.io/caret/train-models-by-tag.html

# Perfomance Metrics 

## Residual 

Deviation of the observed value to the estimated value (sample mean)
$$residual=y_i - \hat{y_i}$$
where $\hat{y_i}$ is the estimated value

## Mean Squared Error (MSE)

$$MSE=\frac{1}{n}\sum_{i=1}^{n}(y_i - \hat{y_i})^2$$

## Root Mean Squared Error (RMSE)
Same units as original data.

$$RMSE=\sqrt{MSE}$$

## L2 regularization : Ridge regression. Regularize by adding the sum of the coefficients, squared, to the function. 

$$Ridge Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p(w_j)^2$$

## L1 regularization : Lasso Regression. Regularize by adding the sum of the absolute value of the coefficients to the model. Coefficient estimates may be pushed to zero -- Lasso can perform variable selection

$$Lasso Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p|w_j|$$


\newpage

### The broad steps of Machine learning in R. 

1. Split the data into training and test. Set test aside. 

2. Fit a good model to the training data. 

3. See how your model did on the training data.

4. Test how your model performs on the test data. 

# Regression

```{r, include=FALSE}
library(caret)
library(MASS)
library(ggplot2)
library(dplyr)
library(ggfortify)


#Mauna Loa CO2 concentrations
data(airquality)

head(airquality)

```


1. Split data into training and test set (75% in train set, 25% in test set)

```{r}
split <- sample(nrow(airquality), floor(nrow(airquality)*0.75))
train_regression = airquality[split,]
test_regression = airquality[-split,]


```


### Linear Regression

* Assumes a linear relationship. 
* Independent variables should not be correlated (no mulitcollinearity)
* The number of observations should be greater than the number of independent variables.


$$RSS=\sum(y_i - \hat{y_i})^2$$
We will predict the response of the Temperature based on Wind. 

This is the data we will fit a linear model to. 
```{r}
# ggplot(data = train_regression) +
#   geom_point(aes(x=Wind, y=Temp)) +
#   theme_bw()
```

2. Create and fit a linear model to predict Temperature from Wind using the training set

```{r}
help(train)

#linear_regression <- train( ~ , data= , method = "lm")

linear_regression <-train( Temp ~ Wind, data= train_regression, method = "lm")
```


3. Vizualize how your model performed on the train data by plotting the regression line on top of the train data points. 
```{r}
ggplot(data = train_regression, aes(x=Wind, y=Temp)) +
  geom_point(aes(x=Wind, y=Temp)) + theme_bw() + geom_smooth(method="lm", col='red')

```


4. Explore how the model performs on the test data. For Linear Regression:

* The residuals should be close to zero.
* There should be equal variance around the regression line (homoscedasticity).
* Residuals should be normally distributed.
* Independent variables and residuals should not be correlated.

4 a) See how the model performs on the test data
```{r}
help(predict)
#linear_predict <- predict(, newdata=)

linear_predict <- predict(linear_regression, test_regression)
```

4 b) Look at the residuals. Are they close to zero?
```{r}
#look at the median residual value. Close to zero is best
help(summary)

summary(linear_regression)

#The median residual is relatively close to zero. It is 1.433.
```


4 c) Plot predicted temperature vs observed temperature. A strong model should show a strong correlation
```{r}
Predicted_vs_Observed <-data.frame(Predicted_Temp= linear_predict, Observed_Temp=test_regression$Temp )

ggplot(data=Predicted_vs_Observed) + geom_point(aes(x=Observed_Temp, y=Predicted_Temp)) + ggtitle("Predicted Model versus Observed Temperatures") + theme_bw()

```

4 d) Visualize the predicted values in relation to the real data points. Look for homoscedasticity
```{r}
# Extract coefficients from the model
coef.intercept <- coef(linear_regression$finalModel)[1]
coef.slope <- coef(linear_regression$finalModel)[2]
# plot the regression line on the predicted values

#plot the original values

ggplot(test_regression, aes(x=Wind, y=Temp)) + geom_point() + geom_point(aes(y=linear_predict), shape=1) + geom_abline(slope = coef.slope, intercept = coef.intercept, col='red') + geom_segment(aes(xend = Wind, yend = linear_predict), alpha = .2) + theme_bw()


plot(fitted(linear_regression), residuals(linear_regression))
#The data is unbiased and homoscedastic due to the large variance when plotting the residuals versus the predicted values.
```

4 e) Residuals should be normally distributed. Plot the density of the residuals
```{r}
#residuals_lin <- residuals(linear_regression)

residuals_lin <- residuals(linear_regression)
plot(density(residuals_lin), main = "Density of Residuals")

#Residuals are normally distributed

#ggplot(data=residvpredict) +
#  geom_density(aes(residual))
```


4 f) Independent variables and residuals should not be correlated
```{r}
#cor.test(train_regression$Wind, resid(linear_regression))

cor.test(train_regression$Wind, resid(linear_regression))

cor.test(train_regression$Temp, resid(linear_regression))
```


### Linear Regression with Regularization

5. Create a linear model using L1 or L2 regularization to predict Temperature from Wind and Month variables. Plot your predicted values and the real Y values on the same plot. 

```{r}
ctrl =  trainControl(method = "boot", 15)

Lasso_regression <- train(Temp ~ Wind + Month, data = train_regression,
                          method = 'lasso', trControl= ctrl) 

Lasso_regression

lasso_test_pred <- predict(Lasso_regression, newdata = test_regression)

#plot the predicted values vs the observed values
plot_lasso_test_pred <- data.frame(Temp_test_pred = lasso_test_pred, 
                                   Observed_Temp = test_regression$Temp)
ggplot(data = plot_lasso_test_pred) +
  geom_point(aes(x=Observed_Temp, y = Temp_test_pred)) + 
  ggtitle("True Temp Value vs Predicted Temp Value Lasso Regression") +
  theme_bw()

#median residual value should be close to zero
median(resid(Lasso_regression))

#Median residual is 0.1387928 and is close to zero.
```



